Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-14 newdraft.tex
Added para-complexification

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\p\!\!\!\p}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}
\paragraph{The para-holomorphic volume form}
In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds. Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.

Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{k,0}(M)$, that is holomorphic, $\bar{\p}\Omega=0$. Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
\begin{Def}
Let $(\PS,K)$ be a para-complex manifold of dimension $2n$. We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
\begin{align*}
\pt \Omega=\p \tl{\Omega}=0.
\end{align*}
\end{Def}
Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.

@@

@@

To determine the corresponding nilpotent operators $\QQ_{V/A}$ on which $V$ and $A$ act trivially, we find that the following combinations of the supercharges
\begin{align*}
Q_{L\pm}=\frac{1}{2}(Q^1_+\pm Q^2_+),\quad Q_{R\pm}=\frac{1}{2}(Q^1_-\pm Q^2_-),
\end{align*}
are all nilpotent and satisfy $[Q_{L\pm},Q_{L\pm}]=0$, so that their sums and differences will also be nilpotent. However, they are charged under the Lorentz group. Their Lorentz charges along with their charges under $SO(1,1)_{V/A}$ are summarized in the following table
\bigskip
\begin{center}
\begin{tabular}{c|c c c}
		& $SO(1,1)_{Lor.}$ & $SO(1,1)_V$ & $SO(1,1)_A$\\ \hline
$Q_{L+}$& $-1$ & $+1$ & $+1$\\
$Q_{L-}$& $-1$ & $-1$ & $+1$\\
$Q_{R+}$& $+1$ & $+1$ & $-1$\\
$Q_{R-}$& $+1$ & $-1$ & $+1$
\end{tabular}.
\end{center}
\bigskip
From the above table, we can read off that the combination $\QQ_V=Q_{L+}+Q_{R-}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_V$ and $\QQ_A=Q_{L+}+Q_{R+}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_A$. Note also that the two are related by $Q_-^2\mapsto -Q_-^2$ and because $Q_-^2=K_-D_-$, this is acheived by changing the sign of $K_-$. Therefore, in the following we will study without loss of generality the twist given by $U(1,1)_A$ and $\QQ_B$, i.e. the generalized para-B-model:

>>>>

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\bm{\p}}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\subsubsection{Para-Complexified Version}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e. $\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e. $Re(x+ky)=x,\ Im(x+ky)=y$.

Therefore, we see that $\mathbf{C}^n$ is a paracomplex vector space with the paracomplex structure given by the multiplication by $k$. Conversely, any $2n$-dimensional paracomplex vector space $(V,K)$ can be identified with $(\mathbf{C}^n,k)$; the $\mathbf{C}$-module structure is defined as $(a+kb)v=av+bK(v)$ and if $(x^i, \xt^i)$ is a basis of $V$ spanning the $\pm 1$ eigenspaces of $K$, then $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ is a basis of $\Cc^n$. In other words, we have the following identification of paracomplex vector spaces
\begin{align}\label{para-complexification}
\begin{aligned}
\begin{array}{ccc}
(\RR^n\times\RR^n,\id \times -\id) &\longleftrightarrow &(\Cc^n, k)\\
(x^i,\xt^i) &\mapsto &\frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i\\
(u^i+v^i,u^i-v^i) &\mapsfrom &u^i+kv^i,
\end{array}
\end{aligned}
\end{align}
where $i=1,\cdots,n$. If $(V,K)$ is a paracomplex vector space, then its paracomplexification, $V\otimes_\mathbb{R} \mathbf{C}\coloneqq V^\Cc$, splits to $\pm k$ eigenspaces of $K$, which is extended to $V^\Cc$ by linearity: $V^\Cc=V^{1,0}\oplus V^{0,1}$. The conjugation map is then an isomorphism between the two eigenspaces, i.e. $\overline{{V^{1,0}}}=V^{0,1}$. The splitting is given by the projections
\begin{align}
\PP^{1,0}=\frac{1}{2}(\id +kK),\quad \PP^{0,1}=\frac{1}{2}(\id -kK). \label{eq:projections_parac}
\end{align}

Let now $(\PS,K)$ be an almost paracomplex manifold. The para-complexified tangent bundle, $T\mathcal{P}^\mathbf{C}=T\mathcal{P}\otimes_\mathbb{R} \mathbf{C}$, splits to a $\pm k$ eigenbundles of $K$ as $T\mathcal{P}^\mathbf{C}=T\mathcal{P}^{1,0}\oplus T\mathcal{P}^{0,1}$. 
%and $T\mathcal{P}^{1,0}$ is isomorphic to $T\PS$ as real vector bundles:
%\begin{align*}
%\begin{aligned}
%\begin{array}{ccc}
%T\PS &\simeq &T\mathcal{P}^{1,0} \\
%X &\longmapsto &\frac{1}{2}(X+kKX) \\
%Re(X^{1,0})=\frac{1}{2}(X^{1,0}+\overline{X^{1,0}})&\longmapsfrom &X^{1,0}
%\end{array}
%\end{aligned}
%\end{align*}
Similarly to the real case, this induces a splitting of $\Lambda^k(T^*\mathcal{P}^\mathbf{C})$:
\begin{align*}
\Lambda^k(T^*\mathcal{P}^\mathbf{C})=\bigoplus_{k=p+q}\Lambda^{p,q}(T^*\mathcal{P}^\mathbf{C}),
\end{align*}
with the sections denoted as $\Omega^{p,q}_\mathbf{C}(\PS)$.
\begin{notation*}
To distinguish between the real and para-complexified bigradings, the former being with respect to the $\pm 1$ eigenvalues of $K$, while the latter is with respect to the $\pm k$ eigenvalues of $K$, we denote the real bigrading in round brackets, $(p,q)$, and the para-complexified grading without brackets, $p,q$.
\end{notation*}

The de-Rham differential also splits accordingly into the \textbf{para-complexified Dolbeault operators}
\begin{align*}
\p^\mathbf{C}&:\Omega^{p,q}_\mathbf{C}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p+1,q}(\mathcal{P}),\\
\bar{\p}^\mathbf{C}&:\Omega_\mathbf{C}^{p,q}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p,q+1}(\mathcal{P})\ .
\end{align*}

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}
\paragraph{The para-holomorphic volume form}
In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds. Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.

Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$. Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
\begin{Def}
Let $(\PS,K)$ be a para-complex manifold of dimension $2n$. We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
\begin{align*}
\pt \Omega=\p \tl{\Omega}=0.
\end{align*}
\end{Def}
Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.

@@

\paragraph{Para-Complexified version}
One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $\TT\otimes_\RR \Cp$. In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
\begin{proposition}
A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
\end{proposition}
\begin{proof}
The proof is entirely analogous to []; if $\KK$ is a generalized paracomplex structure and $L_\KK$ is its $+k$ eigenbundle, $L_\KK$ is automatically maximally isotropic by 
\begin{align*}
\langle x,y \rangle = -\langle\KK x,\KK y \rangle = -\langle k x,k y \rangle = -\langle x,y\rangle=0.
\end{align*}
The para-complex conjugate $\bar{L}_\KK$ is then a $-k$ eigenbundle and $L\cap\bar{L}=0$. Conversely, given $L$ and $\bar{L}$, we can define $\KK$ to be the multiplication by $+k$ on $L$ and $-k$ on $\bar{L}$.
\end{proof}

@@

To determine the corresponding nilpotent operators $\QQ_{V/A}$ on which $V$ and $A$ act trivially, we find that the following combinations of the supercharges
\begin{align*}
Q_{L\pm}=\frac{1}{2}(Q^1_+\pm Q^2_+),\quad Q_{R\pm}=\frac{1}{2}(Q^1_-\pm Q^2_-),
\end{align*}
are all nilpotent and satisfy $[Q_{L\pm},Q_{L\pm}]=0$, so that their sums and differences will also be nilpotent. However, they are charged under the Lorentz group. Their Lorentz charges along with their charges under $SO(1,1)_{V/A}$ are summarized in the following table
\bigskip
\begin{center}
\begin{tabular}{c|c c c}
		& $SO(1,1)_{Lor.}$ & $SO(1,1)_V$ & $SO(1,1)_A$\\ \hline
$Q_{L+}$& $-1$ & $+1$ & $+1$\\
$Q_{L-}$& $-1$ & $-1$ & $-1$\\
$Q_{R+}$& $+1$ & $+1$ & $-1$\\
$Q_{R-}$& $+1$ & $-1$ & $+1$
\end{tabular}.
\end{center}
\bigskip
From the above table, we can read off that the combination $\QQ_V=Q_{L+}+Q_{R-}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_V$ and $\QQ_A=Q_{L+}+Q_{R+}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_A$. Note also that the two are related by $Q_-^2\mapsto -Q_-^2$ and because $Q_-^2=K_-D_-$, this is acheived by changing the sign of $K_-$. Therefore, in the following we will study without loss of generality the twist given by $U(1,1)_A$ and $\QQ_B$, i.e. the generalized para-B-model:
